A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-16 main.tex
Cullen and WHO done

\subsubsection{Holistic health care}
TCGA treated by surgery and more; TNM available yes
discussion: limitation
Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
 since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
the TCGA has not collected holistic features
Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
[Results] In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
%癌症與身心靈的重要關係：中醫、citation? 中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
%自他不二 心存正念
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念
%5.心無恐懼: 情志養生
the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
with more TCGA features
graph convolutional neural network (GCNN)
Wish and bless the whole world

>>>>

\subsubsection{Holistic cancer care}
Bruce Lipton: the biology of belief 信念的力量
biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。
也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。所以我們的科學家依舊在研究，基因對癌症的影響（單向）。
冤親債主的意念
TCGA treated by surgery and more; TNM available yes
discussion: limitation
Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
 since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
the TCGA does not collect holistic features
Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
or even spiritual, emotional, and social status) go holistic

World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic and spiritual perspectives\cite{WHO2015}.
Core principles can be taken to achieve people-centred and integrated health service delivery. First principle is holistic – focusing on physical, socioeconomic, mental and emotional well-being. (Holistic care: care to the “whole person” that considers psychological, social and environmental factors rather than just the symptoms of disease or ill-health)
Second principle is Empowering – supporting people to manage and take responsibility for their own health. (Empowerment: the process of supporting people and communities to take control of their own health needs resulting, for example, in the uptake of healthier behaviours or the ability to self- manage illnesses)
People-centred care requires that people have the education and support they need to make decisions and participate in their own care.
Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

The spiritual care is he key of holistic healthcare in dental practice or for cancer patient.  Being mindful to patient’s mental health and emotional changes during the dental care. Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration.
Learning to listen proactively
9) Therapeutic relationship is an essential key towards spiritual care.
Being aware of patient’s spiritual needs during/after treatment.
12) Applying the holistic healthcare strategies, such as the Shared Decision Marking, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}

Lipton 1992, epinephrine and histamine signals in endothelium, 心智作用
The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.

[Results] In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
PCA and ECA
Carl Rogers: Carl Rogers' person-centered theory
the therapist is providing the appropriate social-environmental conditions \cite{Rogers1957}.\cite{Joseph2004}\cite{Griffiths2013}
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers\cite{Rogers1957}.
The research implication is to investigate the relationship between the client’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
Dealing with negative emotions. As the client feels intense negative emotions of fear, despair, sadness and so on, it is not the client-centred therapist’s task to try and remove these feelings: The task is simply to stay with the client’s experiences. T he research implication is to investigate the necessity and sufficiency of the six conditions.

Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
% http://bibliotecaparalapersona-epimeleia.com/greenstone/collect/ecritos2/index/assoc/HASH01a5/4583605e.dir/doc.pdf

% so do the cancer
Individual treatment and avoiding assumptions. Although it is useful for therapists to have a knowledge of the trauma literature on the general reactions of people who experience trauma, the therapist should not assume that this knowledge necessarily applies to each and every client\cite{Joseph2004}.

Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction,13,16 centred on a physician's therapeutic intentions and his attunement to patient sympathy.
we educate them
1. Mong, L.-C., Liao, F., Chiou, J. & Chiang, P. Tips for Integrating Spiritual Care Delivery in Dental Education. in Asia Pacific Medical Education Conference. Short Communication 5 (National University of Singapore, 2021).\cite{Ling-ChengMong2021}

*** make Figure 5 holistic:
meridian and emotion has mutual reaction
meridian effect tissue and organ
(autonomic nerve system, myofascial network, prefrontal cortex)
placebo-effect influence on drug discovery
博士班學生，越研究越發現，科學的不足
，心理與靈性的力量，更是背後推動的冥冥力量
身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛

騙過你的病-安慰劑效應 The Placebo Effect
(Emmanuelle Sapin, Pascal Goblot)
%1. Sapin, E. & Goblot, P. L’effet placebo (English: The Placebo Effect) [enregistrement vidéo] : le formidable pouvoir de l’auto-guérison. 53 PP-Quebec (Cinéfête, 2014).\cite{Sapin2014}
% https://biblio.bdeb.qc.ca/in/sim/faces/details.xhtml;jsessionid=E3DD39109012D0BEA598E6E5B66A4FD2?id=p::usmarcdef_0000058243&posInPage=8
1. Finniss, D. G. Placebo Effects: Historical and Modern Evaluation. in International review of neurobiology vol. 139 1–27 (2018).\cite{Finniss2018}
%蓋倫劑量 placebo effect 身心靈醫學的核心
In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo. If I had thought of any internal medicine it would have been a dose of the Dover's powders."\cite{Kerr2008}\cite{Finniss2018}.
 (made up of Ipecac and opium) 
 Cullen studied the objective science of analytical chemistry. He also sense that the patient's subjective, psychosomatic or ‘sympathetic constitution’ determined his reaction to a prescribed therapeutic substance.
***Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
Cullen's theory of sympathy is a mind-body function, a kind of ‘vital force’ that animated the human body, coordinated function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
This finely calibrated, rational use of active placebo treatment, in which the physician dispensed a weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine. %啟蒙運動

%sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, whether by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
安慰劑效應的研究，最後導向了良好醫病關係的思考，並成為醫生臨床醫術的元素之一：
「醫師開藥時，其實是把自己當藥方開出去」。
安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
The idea of placebo as a diluted but active substance persisted into the 19th century17 but the term also came to mean a physiologically inert substance - bread or lactose, for example.18,19 Inert substances began to be used in comparative clinical trials during the first half of the 19th century,20 but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.21 This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008}

prefrontal lobe 理智腦 意識 正念 杏仁核
「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
物理作用、信號，雷射針灸

Warburg effect and carcinogenesis
cancer therapy by 患者自癒
Self-Compassion  慈悲
Self-compassion 
除我執
 global self-esteem:
自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}

中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
養生和治療的原則:
一、某些病症可以透過食療而改善的會建議自行調養
二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
四、沒有一勞永逸的食療，不宜執著特定的食療神話
五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
六、認識自己身體的狀態比吸收營養資訊更重要
七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法

repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body

mindfulness and meditation for cancer
情志養生 悲喜憂思苦 七情
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生

ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$

There is much work to be done in investigating the functional relationships more fully.\cite{Rogers1959}

how to do: once holistic feature available, graph convolutional neural network (GCNN) is mandatory: 以免 genomics 光芒萬丈

the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
with more TCGA features

We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on all the TCGA or other in-house cancer datasets.

Wish and bless the whole world
Dali Lama
